Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
fixes
saving

The contributions of this work are as follows \Sof{Finish this}:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
   \item A tool that implements \comb{}.
	%\item Empirical evidence that the \comb{} combination improves
\end{itemize}

@@

This section discusses  important background material for the rest of the paper.
\Rui{not very happy with this sentence.}

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available at \Rui{site}.

@@

Spectrum-based fault localization is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in
fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
following are given in \sfl{}: a finite set $\mathcal{C}=\set{c_1,c_2,...,c_M}$ of $M$ system \emph{components}\footnote{A
  component can be any code artifact of arbitrary granularity
  such as a class, a method, or a statement~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an
$N\times{}M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the
coverage of component $c_j$ in transaction $t_i$.  The pair
$(\mathcal{A},e)$ is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{2}{0.3\textwidth}
  \hspace{-2ex}
  \centering
  \scriptsize
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}

@@

In the following, we illustrate the workflow of the \sfl{}+\cs{}
combination for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the workflow of the
\comb{} approach consists of four steps: \Sof{Should we
  specify that these steps are performed for each version of the
  projects/defect?}\Mar{Isn't this clear from the scenario in the
  beginning of par?  Note that this is the definition of the workflow
  for the technique, not the definition of the experiment (when it
  makes sense to talk about versions/defects and D4J.)}\Rui{agree with Marcelo.}
  \Rui{if space permits, a figure with the workflow might be good.}

\begin{enumerate}
  \itemsep0em
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious source
  files\Rui{classes?}, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
    \Rui{union of slices of all points ?}
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
\end{enumerate}

@@

To evaluate our approach, we compare the cost of diagnosing
a collection of faulty versions using \sfl{} versus \comb{}.

@@

Recall from Section~\ref{sec:approach} that the \comb{}
takes as input a value $k$ that denotes the $k$ most suspicious distinct
classes to be considered. To evaluate the effectiveness of \comb{}, following
related work, we compared its
performance with \sfl{} for each defect on each subject program from
the dataset, for $k\in\{5,10\}$. These classes are obtained directly
from the ranking. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{} using the
following metrics.\Mar{Sofia, I don't see a reason for an equation to
  only show the difference of cost. Please describe precisely the
  metrics. In this case, I can't find what C stands for. Also,
 you need to describe precisely what top@n (or someother name) means
 in this context. Check if it makes sense for SFL.$\rightarrow$}\Rui{It might
 be good to keep it just to give it some emphasis... }

@@

\noindent
where $C$ is the cost of diagnosis. \Rui{At this point, you need to explain what
the cost of diagnosis is: C is the number of statemetns (?) that need to be
inspected before finding the fault, right? We also need to say that we assume a
perfect bug understanding: that is, when the developer sees the bug in the
ranking, he can say that it is the faulty one.}
A positive $\Delta$C means that the position of the faulty statement has decreased
in the ranking reported computed by \combpar{k}. Hence, reducing the cost to
find the bug.

@@

\begin{table*}[h]
	\centering
	  \begin{tabular}{|l|ccc|cccc|c|}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{SFL+DS-$k$} & \multirow{2}{*}{\# Faults} \\

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\
		\midrule
		 \lang{}            & 84.1\%  & 84.1\%  &  0\%   & 63 & 100\% & 61 & 96.8\% & 63      \\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and SFL+DS-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
  \label{table:fsws}
\end{table*}

% \begin{table*}[h]
% 	\centering
% 	\setlength{\tabcolsep}{4pt}
% 	\begin{tabular}{llllll}
% 		\toprule
% 		Project             &  \# top-5  & \% top-5 & \# top-10 & \% top-10 & \# Faults \\
% 		\midrule
% 		\chart{}  & 20 & 76.92\% & 22 & 84.62\%  & 26\\
% 		\jtime{}  &  &  &  &   & \\
% 		\bottomrule
% 	\end{tabular}
% 	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
% 	\label{tab:fs}
% \end{table*}
% \normalsize

>>>>

The contributions of this work are the following ones:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
   \item A tool that implements \comb{}.
\end{itemize}

@@

This section summarizes the ground concepts of our approach.

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available at \textit{$<$anonymized for double-blind review$>$}.

@@

\begin{wrapfigure}[8]{2}{0.3\textwidth}
  \hspace{-2ex}
  \centering
  \scriptsize
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}

Spectrum-based fault localization is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in
fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
following are given in \sfl{}: a finite set $\mathcal{C}=\set{c_1,c_2,...,c_M}$ of $M$ system \emph{components}\footnote{A
  component can be any code artifact of arbitrary granularity
  such as a class, a method, or a statement~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an
$N\times{}M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the
coverage of component $c_j$ in transaction $t_i$.  The pair
$(\mathcal{A},e)$ is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.

@@

In the following, we illustrate the workflow of the \comb{}
approach for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the workflow of the
\comb{} approach consists of four steps: 
\begin{enumerate}
  \itemsep0em
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious source
  files\Rui{classes?}, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
    \Rui{union of slices of all points ?}
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
\end{enumerate}

@@

To evaluate our approach, we compare the cost of diagnosing
a collection of faulty versions using \sfl{}
against \comb{}.

@@

Recall from Section~\ref{sec:approach} that the \comb{} combination
takes on input a value denoting the $k$ most suspicious distinct
files. To evaluate the effectiveness of \comb{}, we compared its
performance with \sfl{} for each defect on each subject program from
the dataset, for $k\in\{5,10\}$. These files are obtained directly
from the ranking. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{} using the
following metrics.\Mar{Sofia, I don't see a reason for an equation to
  only show the difference of cost. Please describe precisely the
  metrics. In this case, I can't find what C stands for. Also,
 you need to describe precisely what top@n (or someother name) means
 in this context. Check if it makes sense for SFL.$\rightarrow$}

@@

where C is the cost of diagnosis. \Sof{@todo: Explain this better in section 2 or 3}
A positive $\Delta$C means that the faulty statement has risen in
the ranking reported by \sfl{} techniques when \ds{} is used,
producing a reduced cost of diagnosing.

%% Firstly, we ran the dataset presented in Section~\ref{sec:analysis}
%% with \sfl{} to gather the coverage statements ordered from the highest
%% faulty statement to the lowest faulty statement. This list is the
%% input of the \comb{} technique. For each defect, the list is evaluated
%% in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source
%% files. Then, Lithium minimizes each source file for each testcase of
%% the defect considering the top-$5$ (\comb{}-$5$) and top-$10$
%% (\comb{}-$10$) of source files separately. Some defects have more than
%% one testcase. In the end, we update spectra $S$ based on the output of
%% the minimization as presented in Figure~\ref{fig:ds-reduction} to
%% obtain the faulty statements ranking after minimization. All scripts
%% used to run these experiments and gather data are available at
%% \url{TBA} and \url{TBA}, respectively.

%% \Sof{Parei Aqui}

@@

\begin{table*}[h]
	\centering
	  \begin{tabular}{|l|ccc|cccc|c|}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{\comb{}-$k$} & \multirow{2}{*}{\# Faults} \\

		            & \% top-5 & \% top-10  & $\Delta$ & \# top-5 & \% top-5 & \# top-10 & \% top-10 &  \\
		\midrule
		 \lang{}            & 84.1\%  & 84.1\%  &  0\%   & 63 & 100\% & 61 & 96.8\% & 63      \\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \comb{}-$k$ report \Sof{@todo: Add absolute numbers for SFL}}
  \label{table:fsws}
\end{table*}
